Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-05-15 eval.tex
Changed some things.

Figure~\ref{fig:haversine} demonstrates the result of combing the measured
signal strength values, together with the harvesine function enables us to
calculate the distance from the point where maximum signal has been
capture.

@@

\subsection{Communication Performance}
In this experiment, we present some preliminary results to evaluate the communication
performance of our system.  In the experiment, we varied the bitrate of the transmitter
from 1 bit/s up to 1 kbit/s. As we had seen earlier in the Figure~\ref{fig:transmission}, the strength
of the backscattered signal is rather low leading to the appearance of significant quantisation noise.
We improve the situation by increasing the analog gain of the receiver, and perform
the experiment with the maximum gain \SI{50}{\decibel} available at out receiver.

In an indoor environment, where the ambient signal strength is low, we are
able to achieve a data rate of 1 b/s with distances of
couple of meters. At higher bitrates, we observe a range of few 
few decimeters and the  bit error rate is still approximately 40 \%. 
We observed similar results outdoors. We acknowledge the high bit errors
observed due to primarily limited gain available on the low cost dongles.
In future, we will work to improve this. We note, existing ambient backscatter
systems do not operate well indoors at large distances, and our results
provide preliminary results of  improvements possible by leveraging low-cost
SDRs.

>>>>

Figure~\ref{fig:haversine} demonstrates the result of combing the measured
signal strength values, together with the haversine function enables us to
calculate the distance from the point where the maximum signal has been
captured. The fast fading of the signal has been proven to be highly fluctuating, but it is still hight enough to enable backscattering.

@@

\subsection{Communication Performance}
In this experiment, we present some preliminary results to evaluate the communication
performance of our system.  In the experiment, we varied the bitrate of the transmitter
from 1 bit/s up to 1 kbit/s. As we had seen earlier in the Figure~\ref{fig:transmission}, the strength
of the backscattered signal is rather low leading to the appearance of significant quantisation noise.
The experiments have been carried out with the maximum gain available from the tuner of \SI{50}{\decibel}.

In an indoor environment, where the ambient signal strength is low, we are
able to achieve a data rate of 1 b/s with distances of
couple of meters. At higher bitrates, we observe a range of a few decimeters and the  bit error rate is still approximately 40 \%. 
We observed similar results outdoors. We acknowledge the high bit errors
observed due to primarily limited gain available on the low cost dongles.
In future, we will work to improve this. We note, existing ambient backscatter
systems do not operate well indoors at large distances, and our results
provide preliminary results of  improvements possible by leveraging low-cost
SDRs.

### 2017-05-15 paper.tex
Changed some things.

\includegraphics[width=\columnwidth]{./fig/transmission}
\vspace{-30mm}
\caption{Data from the Octave oscilloscope showing the start of a transmission of 101010.. with 1 kbit/s with idle state before. The amplitude is quite low with an average of 12 \% of the maximum, which is 127.5. This is due to a low signal strength. Sampling frequency is 25 kHz. At the top one can see the raw signal from the ADC, in the middle the filtered signal and at the bottom the signal after the Schmitt trigger.}
\label{fig:transmission}
\vspace{-6mm}

>>>>

\includegraphics[width=\columnwidth]{./fig/transmission}
\vspace{-30mm}
	\caption{\emph{Plots from Octave oscilloscope showing the start of a transmission of 101010..} In the top plot one can see the raw analog signal, in the middle plot the filtered signal and finally at the bottom the signal after processing though the Schmitt trigger. The amplitude is quite low with an average of 12 \% of the maximum, which is 127.5 due to a low signal strength. Sampling frequency is 25 kHz. }
\label{fig:transmission}
\vspace{-6mm}
